\pkg{disaggregation}: An \proglang{R} Package for Bayesian Spatial Disaggregation Modelling

### 2020-02-14 article.Rnw
Add \pkg, \proglang, \code formatting for titles and references

\title{disaggregation: An \proglang{R} Package for Bayesian Spatial Disaggregation Modelling}
\Plaintitle{disaggregation: An R Package for Bayesian Spatial Disaggregation Modelling}
\Shorttitle{Disaggregation Modelling in \proglang{R}}

@@

\Keywords{Bayesian spatial modelling, disaggregation modelling, TMB}
\Plainkeywords{Bayesian spatial modelling, disaggregation modelling, TMB}

>>>>

\title{\pkg{disaggregation}: An \proglang{R} Package for Bayesian Spatial Disaggregation Modelling}
\Plaintitle{disaggregation: An R Package for Bayesian Spatial Disaggregation Modelling}
\Shorttitle{Disaggregation Modelling in \proglang{R}}

@@

\Keywords{Bayesian spatial modelling, disaggregation modelling, TMB}
\Plainkeywords{Bayesian spatial modelling, disaggregation modelling, \pkg{TMB}}
